\cvsection{Projects}

\begin{cventries}

    
     \cventry
    {Personal Project} % Organization
    {{My Job Hunt Tracker}} % Job title
    {\href{https://react-jobsearchapp.web.app/}{Project Link } \href{https://github.com/zmiguel2016/jobSearchApp}{ Code Link}} % Location
    { Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created a web application designed to keep track of the job application process from finding a job, interviewing, coding exams, and final decision.}
        \item {Implemented Github Job API to create a live feed of up to 50 accessible job postings per page which can be added to the users job tracker list.}
        \item {Integrated user-authentication and back-end database to keep track of unique users progress}
        \item {Tech Stack: React JS, Github Jobs API, Firebase, Git Version Control }
      \end{cvitems}
    }

    \cventry
    {University of South Carolina} % Organization
    {{CISA Mobile Conference Application}} % Job title
    {\href{https://sccapstone.github.io/TheClimateCrew/index}{Project Link}} % Location
    {Aug. 2019 - May. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for communicating design aspects with clients and then laying out a hand-drawn and digital preview of UI/UX design to be approved by  the client.}
        \item {Responsible for testing and building the release for IOS devices.}
        \item {Created a robust calendar feature that displays events the user has signed up for from the database in real-time.}
        \item {Took responsibility for debugging and assigning issues to a corresponding teammates.}
        \item {Tech Stack: Angular9, Ionic Framework, Firebase, Git Version Control }
      \end{cvitems}
    }

    \cventry
    {University of South Carolina} % Organization
    {{Vibe Check Social Media Application}} % Job title
    {\href{https://youtu.be/b_Kv6etAXbw}{Project Link } \href{https://github.com/zmiguel2016/vibeCheck}{ Code Link}} % Location
    {Jan. 2020 - May. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Took responsibility for assigning task and issues to team members to complete.}
        \item {Responsible for testing, debugging, and deploying the application.}
        \item {Set up back-end database function calls and user authentication with Google Firebase.}
         \item {Created overall UI design and layout for the social feed page and user friends page.}
         \item {Tech Stack: Angular9, Ionic Framework, Firebase, Git Version Control }
      \end{cvitems}
    }
    
\end{cventries}